### 2015-05-05 conclusion.tex
daily update

>>>>

\citet{Xenakis20063225}

\paragraph{Disk encryption}
As the hardware is better used with larger blocks of data, disk encryption could be an interesting application to look into.

\paragraph{Cryptographic libraries}
OpenSSL is not the only cryptographic library available; PolarSSL and GnuTLS could also be viable solutions.
%TODO see if they can use cryptodev, that would be perfect.

\paragraph{Cryptodev}
If patches adding the GCM support to cryptodev have already been released, those are not compatible with Barco Silex' driver.
Adapting the interface would open the GCM hardware offload to the whole user space applications park.

\paragraph{MAC offloading}
While the symetric and asymetric encryption ciphers IPs are usable from the operating system, the IP computing MACs does not have a usable driver yet.
Wherever there is encryption, authentication is also needed.
As such, any real day-to-day use case can not be fully offloaded to hardware yet, even if some tricks and patches allowed us to bypass this requirement.
The implementation of the GCM mode, combining encryption and authentication, showed us that stopping relying on the software implementation of MACs would be a huge step forward.
